Different rules for binocular combination of luminance flicker in cortical and subcortical pathways

### 2023-06-09 manuscript.Rmd
Added lines at the beginning to link to figures (and not to captions) and to link to references.

---
title: "Different rules for binocular combination of luminance flicker in cortical and subcortical pathways"
author: |
 | Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade &  Daniel H. Baker
 | Department of Psychology, University of York, UK
 | *eLife* (2023) https://doi.org/10.7554/eLife.87048
output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
    keep_tex: yes
  word_document2: default
  html_document: default
bibliography: references.bib
csl: elife.csl
header-includes:
- \usepackage{float}
- \usepackage{float} \floatplacement{figure}{H}
- \newcommand{\beginsupplement}{\setcounter{table}{0}
- \renewcommand{\thetable}{A\arabic{table}}
- \setcounter{figure}{0}
- \renewcommand{\thefigure}{A\arabic{figure}}}
---

@@

processdata <- 2  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data
# 2 - average data across participants, do bootstrapping
# 3 - download all raw data and analyse (requires 48GB of storage)

domodelling <- 1    # if set to 1, run the Stan models (takes ~24 hours)

>>>>

---
title: "Different rules for binocular combination of luminance flicker in cortical and subcortical pathways"
author: |
 | Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade &  Daniel H. Baker
 | Department of Psychology, University of York, UK
 | *eLife* (2023) https://doi.org/10.7554/eLife.87048
output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
    keep_tex: yes
  word_document2: default
  html_document: default
bibliography: references.bib
link-citations: true
csl: elife.csl
header-includes:
- \usepackage{float}
- \usepackage{float} \floatplacement{figure}{H}
- \newcommand{\beginsupplement}{\setcounter{table}{0}
- \renewcommand{\thetable}{A\arabic{table}}
- \setcounter{figure}{0}
- \renewcommand{\thefigure}{A\arabic{figure}}}
- \usepackage{caption}
---

@@

processdata <- 0  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data
# 2 - average data across participants, do bootstrapping
# 3 - download all raw data and analyse (requires 48GB of storage)

domodelling <- 0    # if set to 1, run the Stan models (takes ~24 hours)
